The Blessing of FedAvg's Linear Speedup in Federated Learning

### 2020-05-31 source/sec_relatedwork.tex
updated reference

\textbf{The Convergence of FedAvg and Linear Speedup}
There has been a vast amount of convergence analysis for Federated averaging
(FedAvg) in different settings. However, most of the prior works provide the
convergence guarantee under the simplified setting, where either statistical
heterogeneity~\cite{stich2018local} or system
heterogeneity~\cite{yu2019parallel,wang2019adaptive,khaled2019first} are not
considered. This simplified setting is also referred as local SGD. 
In~\cite{li2019convergence},
the authors firstly provide convergence of FedAvg for strongly convex problem considering both statistical heterogeneity and system heterogeneity, while their results
didn't achieve linear speedup. In~\cite{haddadpour2019convergence,liang2019variance,huo2020faster}, the convergence of FedAvg for non-convex problems has been studied. 
However, \cite{huo2020faster} did not discuss the linear speedup and the theorems in \cite{haddadpour2019convergence,liang2019variance} failed to cover the accelerated version of
FedAvg.

>>>>

\textbf{The Convergence of FedAvg and Linear Speedup}
There has been a vast amount of convergence analysis for Federated averaging
(FedAvg) in different settings. However, most of the prior works provide the
convergence guarantee under the simplified setting, where either statistical
heterogeneity~\cite{stich2018local,zhou2017convergence,wang2018cooperative,woodworth2018graph} or system
heterogeneity~\cite{yu2019parallel,wang2019adaptive,khaled2019first,jiang2018linear} are not
considered. This simplified setting is also referred as local SGD. 
In~\cite{li2019convergence},
the authors firstly provide convergence of FedAvg for strongly convex problem considering both statistical heterogeneity and system heterogeneity, while their results
didn't achieve linear speedup. In~\cite{haddadpour2019convergence,liang2019variance,huo2020faster,jiang2018linear}, the convergence of FedAvg for non-convex problems has been studied. 
However, \cite{huo2020faster} did not discuss the linear speedup and the theorems in \cite{haddadpour2019convergence,liang2019variance} failed to cover the accelerated version of
FedAvg.
